An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-18 indicators/paper/paper.tex
Incorporate some of Nigam's language on public health
To make our contributions to public health clearer.

Auxiliary signals (outside of the standard public health reporting streams) can
serve as indicators of COVID activity, but they can also illuminate other
aspects of the pandemic. To understand the effect of the pandemic on society and
predict its future spread requires a comprehensive view of not just cases and
deaths, but public behavior and beliefs. Measures of mobility reflect social
distancing policies and the potential rate of COVID spread; medical claims data
reflects healthcare-seeking behavior and how it may be affected by local case
rates; measures of COVID vaccine acceptance can guide outreach efforts.

@@

Finally, we emphasize that unifying many relevant signals into a single common
format, with comprehensive revision tracking, is a valuable goal in and of
itself. No one data source is perfect; each is subject to error. Bringing
numerous signals from different data streams all together, and making access as
convenient as possible for public health researchers, policy makers, modelers,
etc., is a strong testament to our belief that ``the whole is greater than the
sum of its parts''.

>>>>

Auxiliary signals (outside of the standard public health reporting streams) can
serve as indicators of COVID activity, but they can illustrate the effect of
mitigating actions (such as shelter-in-place orders) and can guide resource
allocation for fighting the pandemic. For example, medical claims data reflects
healthcare-seeking behavior; measures of mobility reflect adherence to public
health recommendations; and measures of COVID vaccine acceptance can guide
outreach efforts.

@@

Finally, we emphasize that unifying many relevant signals into a single common
format, with comprehensive revision tracking, is a valuable goal in and of
itself. The ability to combine public health reporting data, syndromic
surveillance data, and digital surveillance measures of mobility and behaviors
creates a platform that goes beyond providing situational awareness. Providing
convenient and real-time access to this data provides continuous telemetry
summarizing how things are, how they are expected to change, which areas need
additional resources to be allocated in response, and how effective public
communication is.
